ms_willow_network_supplement

### 2015-04-20 ms_willow_network_supplement.Rmd
first complete draft of network manuscript and supplementary info

>>>>

```{r}
gall.corrs.df <- full.df %>% select(Genotype, vLG.height.mean, vLG.gall.count, vLG_abund, rG_abund, aSG_abund)
gall.corrs.pheno <- select(gall.corrs.df, -Genotype, -vLG.gall.count)
library(psych)
library(car)
scatterplotMatrix(gall.corrs.pheno)
corr.test(gall.corrs.pheno, use = "pairwise", method = "pearson")

gall.corrs.geno <- gall.corrs.df %>%
  group_by(Genotype) %>%
  summarise(leaf_gall_size = weighted.mean(vLG.height.mean, vLG.gall.count, na.rm = TRUE),
            leaf_gall_abund = mean(vLG_abund, na.rm = TRUE),
            bud_gall_abund = mean(rG_abund, na.rm = TRUE),
            apical_stem_gall_abund = mean(aSG_abund, na.rm = TRUE)) %>%
  select(leaf_gall_size, leaf_gall_abund, bud_gall_abund, apical_stem_gall_abund)
scatterplotMatrix(gall.corrs.geno)
corr.test(gall.corrs.geno)
```
